Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-01-11 manuscript.tex
Add workflow graph [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/c207190574a67d3ccfd31e91a7e5f576d32f7261.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/c207190574a67d3ccfd31e91a7e5f576d32f7261/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/477484908

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...9bba6f14f1c6151dcef6a858c1d33aa070a70b5c}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/9bba6f14f1c6151dcef6a858c1d33aa070a70b5c/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/9bba6f14f1c6151dcef6a858c1d33aa070a70b5c}{habi/zmk-tooth-cohort-method-manuscript@9bba6f1}
on December 21, 2020.

@@

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. CC 810.30 Federal Act of 30 September 2011 on Research involving Human Beings (Human Research Act, HRA). \url{https://www.admin.ch/opc/en/classified-compilation/20061313/index.html}. Accessed 21 Dec 2020.
\end{cslreferences}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...c207190574a67d3ccfd31e91a7e5f576d32f7261}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/c207190574a67d3ccfd31e91a7e5f576d32f7261/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/c207190574a67d3ccfd31e91a7e5f576d32f7261}{habi/zmk-tooth-cohort-method-manuscript@c207190}
on January 11, 2021.

@@

The whole workflow performed for this manuscript is depicted in Figure \ref{fig:workflow}.
Details of each step are explained in this section.

\begin{figure}
\hypertarget{fig:workflow}{%
\centering
\includegraphics{images/workflow.png}
\caption{Workflow of steps performed for this manuscript.}\label{fig:workflow}
}
\end{figure}

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. CC 810.30 Federal Act of 30 September 2011 on Research involving Human Beings (Human Research Act, HRA). \url{https://www.admin.ch/opc/en/classified-compilation/20061313/index.html}. Accessed 11 Jan 2021.
\end{cslreferences}
